---
title: "index"
author: "Gemma"
date: "11/30/2017"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdow document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r install, include = FALSE}
library(tidyverse)

```

## Scatter plot
```{r scatterplot}
library(tidyverse)


ggplot(data = mpg, aes(displ, hwy)) + 
  geom_point()

```

## Scatter with colour 

```{r colour fig}
ggplot(data = mpg, aes(displ, hwy, colour = class)) + 
  geom_point()
```

## Scatter b&w

```{r b&w fig}
ggplot(data = mpg, aes(displ, hwy, size = class)) + 
  geom_point()
```

## Scatter alpha 
```{r alpha}
ggplot(data = mpg, aes(displ, hwy, size = class, colour = fl)) + 
  geom_point(alpha = 0.4)
```

## Boxplot
```{r boxplot}

ggplot(mpg, aes(drv, hwy)) + 
  geom_boxplot()
```

## Violin plot
```{r violin}

ggplot(mpg, aes(drv, hwy)) + 
  geom_violin()
```

## Scatterplot with smooth

```{r scatterplot smooth}


ggplot(data = mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth(method = 'gam', formula = y ~ s(x)) + 
  labs(title = "relationship between engine displacement and highway MPG",  x = "displacement", y = "Highway MPG") + 
  theme_bw()

```